pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-20 article.tex

We start with an idealised birth-death tree of five taxa and a crown age of 10:

@@

This time, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branch lengths follow
an idealized \giovanni{I don't think this is true. A twin tree is generated randomly. If we use the method "maxlikelihood" (see the function "createbdtree") the tree will be chosen in such a way it will maximizing the likelihood with the parameters we estimated from the original tree, but I would not call it "idealized". Furthermore I think it's not obvious to use the "maxlikelihood" method, as in general the "ideal" scenario should be established using a distribution of trees. A single tree is always the result of a stochastic process.} birth-death distribution. Creating a twinning parameter is easy,
as it has sensible default settings:

>>>>

We start with an idealised \giovanni{I still don't get why we need an "idealized" tree.} birth-death tree of five taxa and a crown age of 10:

% Need idealised birth-death tree
% From https://github.com/richelbilderbeek/pirouette_article/issues/1
% and https://github.com/richelbilderbeek/pirouette/issues/35
\begin{lstlisting}[language=R, floatplacement=H, frame=single]
phylogeny <- ape::read.tree(text = "((A:7.1,(B:2.2,C:2.2):4.9):2.9,(D:4.6,E:4.6):5.4):0;")
\end{lstlisting}

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_bd.png}
  \caption{pippo}
\end{figure}

@@

This time, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branch lengths follow
an idealized \giovanni{I don't think this is true. A twin tree is generated randomly. If we use the method "maxlikelihood" (see the function "createbdtree") the tree will be chosen in such a way it will maximizing the likelihood given the parameters we estimated from the original tree, but I would not call it "idealized". Furthermore I think it's not obvious to use the "maxlikelihood" method, as in general the "ideal" scenario should be established using a distribution of trees. A single tree is always the result of a stochastic process.} birth-death distribution. Creating a twinning parameter is easy,
as it has sensible default settings:
